### 2021-04-08 input/conclusion.tex
text of first experiment
rework issue with delete

@@

>>>>

In this paper, we proposed a general purpose definition of scoped
broadcast, and an extension to automatically adapt the scope of scoped
broadcast in contexts where each process can decide whether or not it
decide to be a source. We proposed an implementation called \NAME.

@@

\noindent We propose an implementation that further decreases
generated traffic and improves on
anonymity~\cite{whitaker2002forwarding}.  \NAME makes extensive use of
paths to enable deleting messages without incrementing local
counters. Messages carry their respective path and processes detect
when such messages have been looping when they carry their identity
(see Lines~\ref{line:notloopingA} and \ref{line:notloopingB} of
Algorithm~\ref{algo:adddelundo}). Since membership is all that
matters, we propose to trade vectors of identities for Bloom
filters~\cite{almeida2007scalable}. Processes know with high
probability if they already received and forwarded each message
without knowing the identity of all processes that received it.  False
positive probability only incurs premature stopping of broadcast
messages and does not invalidate the delete of specific
messages. \TODO{Rework.}

### 2021-04-08 input/figproblemB.tex
rework issue with delete

  \draw (-\X + 5pt, 0) --
  node[above=-0.3em,font=\tiny]{$\DEL_{a} \rightarrow$}
  node[below=-0.3em,font=\tiny]{$\leftarrow \ADD_{a}^{3}$}
  (0 - 5pt, 0); %% b - a

  \draw (0 +5pt, 0) --
  node[above=-0.3em, font=\tiny]{$\leftarrow \textcolor{\PC}{\ADD_{c}^{1}}\cdot\DEL{c}$}
  node[below=-0.3em, font=\tiny]{$\textcolor{\PA}{\ADD_a^{2.5}} \rightarrow$}
  (\X -5pt, 0); %% b - c

  \draw[opacity=0] (0, 0 - 5pt) --
  node[opacity=1, above=-0.3em, font=\tiny, sloped]{$\ADD_a^{2.5} \rightarrow$}
  (0, \Y + 5pt); %% b - d
  \draw (0, \Y + 5pt) --
  node[above=-0.3em, font=\tiny, sloped]{$\ADD_c^2 \rightarrow$}
  (0, 0 - 5pt);  %% d - b

  \draw (\X + 3pt, 0 - 5pt) --
  node[above=-0.3em, font=\tiny, sloped]{$\ADD_{c}^{2} \rightarrow$}
  node[below=-0.3em, font=\tiny, sloped]{$\leftarrow \DEL_c$}
  (0 + 5pt, \Y - 3pt); %% c - d

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node[color=\PA]{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node[color=\PC]{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  % \draw (-\X+5pt, 5pt) node[above left]{$\DEL_a$};
  % \draw (\X+5pt, 5pt) node[above right]{$\DEL_c$};
  \draw (0, 5pt) node[above]{$\bm{a: 1.5}$};
  \draw (-5pt, \Y) node[left]{$\bm{c: 1}$};

>>>>

  \draw (-\X + 5pt, 0) --
  node[above=-0.3em,font=\tiny]{$\DEL_{a} \rightarrow$}
  % node[below=-0.3em,font=\tiny]{$\leftarrow \ADD_{a}^{3}$}
  (0 - 5pt, 0); %% b - a

  \draw (0 +5pt, 0) --
  node[above=-0.3em, font=\tiny]{$\leftarrow \textcolor{\PD}{\ADD_{d}^{4}}\cdot\DEL_{d}$}
  node[below=-0.3em, font=\tiny]{$\textcolor{\PA}{\ADD_a^{3}} \rightarrow$}
  (\X -5pt, 0); %% b - c

  \draw[opacity=0] (0, 0 - 5pt) --
  node[opacity=1, above=-0.3em, font=\tiny, sloped]{$\textcolor{\PA}{\ADD_a^{3}} \rightarrow$}
  (0, \Y + 5pt); %% b - d
  \draw (0, \Y + 5pt) --
  node[above=-0.3em, font=\tiny, sloped]{$\DEL_d \cdot \textcolor{\PD}{\ADD_d^1} \rightarrow$}
  (0, 0 - 5pt);  %% d - b

  \draw (\X + 3pt, 0 - 5pt) --
  % node[above=-0.3em, font=\tiny, sloped]{$\ADD_{c}^{2} \rightarrow$}
  % node[below=-0.3em, font=\tiny, sloped]{$\leftarrow \DEL_c$}
  (0 + 5pt, \Y - 3pt); %% c - d

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node[color=\PA]{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X+5pt, 5pt) node[above, font=\small]{$\alpha_a \rightarrow \DEL_a$};
  \draw (\X, 5pt) node[above, font=\small]{$\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};
  \draw (0, 5pt) node[above, font=\small]{$\textcolor{\PA}{\ADD_a^{2}}$};
  \draw (-5pt, \Y) node[left, font=\small]{$\ADD_d \rightarrow \DEL_d$};

### 2021-04-08 input/proposal.tex
rework issue with delete

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system. All processes
that belong to this partition must eventually choose another partition
to belong to. In Figure~\ref{fig:del}, two partitions exist initially:
$P_a$ and $P_c$ that respectively include $\{a\}$, and $\{b, c,
d\}$. In Figure~\ref{fig:delA}, Process $a$ deletes its partition. It
notifies all neighboring processes -- here only Process $b$ -- that
may belong to its partition using \NAMEB. Upon receipt, Process $b$
discards the message $\delta_a$, for the latter does not target the
former's partition. Yet, Process $b$ sends its own partition that may
be the best for Process $a$. Eventually, every processes belong to the
same partition $P_c$.

@@

@@

Algorithm~\ref{algo:adddelundo} provides the instructions that
implement dynamic consistent partitioning:
\begin{inparaenum}[(i)]
\item \label{algo:most} most of the time, it propagates $\alpha$'s and
  $\delta$'s when the partitions allow it;
\item \label{algo:sometimes} sometimes, it detects possible
  inconsistent partitioning and
\item \label{algo:solves}solves it using propagation trees (as opposed
  to propagation graphs);
\item \label{algo:competition} when required, it triggers competitions
  among neighboring partitions.
\end{inparaenum}
While (\ref{algo:most})-(\ref{algo:solves}) tackle the eventual purging of
stale notifications, (\ref{algo:competition}) tackle the eventual
delivery of the best up-to-date partitions.

\paragraph{Dynamic partitions.}
We extend Algorithm~\ref{algo:add} to enable each source to revoke its
self-appointed status of source and become a simple process again. In
that regard, we enforce the delivery order of messages at each
process.

To implement last win order, each process maintains a vector of
versions that associates to each known source, or has-been source, its
known local counter. It enables processes to deliver only up-to-date
$\alpha$'s that may improve their best known partition (see
Line~\ref{line:detectA}), but also to detect possible inconsistent
partitioning (see Line~\ref{line:detectB}) as labeled by III in
Figure~\ref{fig:proofB}. From a global perspective, it ensures
monotonic increase of knowledge despite the non-monotonic number of
sources. In turns, it contributes to convergence and termination, for
corresponding $\alpha$ and $\delta$ cannot follow each other in an
infinite loop.

@@

\paragraph{Dynamic network.}
Algorithm~\ref{algo:edges} provides the instructions of \NAME that
enable dynamic consistent partitioning in dynamic networks where
processes can join or leave the system without
notification. \TODO{More.}

@@

\paragraph{Another trade-off.}
We propose an implementation that further decreases generated traffic
and improves on anonymity~\cite{whitaker2002forwarding}.  \NAME makes
extensive use of paths to enable deleting messages without
incrementing local counters. Messages carry their respective path and
processes detect when such messages have been looping when they carry
their identity (see Lines~\ref{line:notloopingA} and
\ref{line:notloopingB} of Algorithm~\ref{algo:adddelundo}). Since
membership is all that matters, we propose to trade vectors of
identities for Bloom filters~\cite{almeida2007scalable}. Processes
know with high probability if they already received and forwarded each
message without knowing the identity of all processes that received
it.  False positive probability only incurs premature stopping of
broadcast messages and does not invalidate the delete of specific
messages.

>>>>

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system, by executing a
\texttt{Del} operation. All processes that belong to this partition
must eventually choose another partition to belong to. In
Figure~\ref{fig:del}, two partitions exist initially: $P_a$ and $P_c$
that respectively include $\{a\}$, and $\{b, c, d\}$. In
Figure~\ref{fig:delA}, Process $a$ deletes its partition. It notifies
all neighboring processes -- here only Process $b$ -- that may belong
to its partition using \NAMEB. Upon receipt, Process $b$ discards the
message $\delta_a$, for the latter does not target the former's
partition. Yet, Process $b$ sends its own partition that may be the
best for Process $a$. Eventually, every processes belong to the same
partition $P_c$.

@@

\begin{proof}
  \TODO{Quite obvious.}
\end{proof}

\begin{theorem}[\TODO{meow}]
  \TODO{Puring stale notifications requires to handle I...IV.}
\end{theorem}

@@

We extend Algorithm~\ref{algo:add} to enable each source to revoke its
self-appointed status of source and become a simple process again.
Algorithm~\ref{algo:adddelundo} provides the instructions that
implement dynamic consistent partitioning:
\begin{inparaenum}[(i)]
\item \label{algo:most} most of the time, it propagates $\alpha$'s and
  $\delta$'s when the partitions allow it;
\item \label{algo:sometimes} sometimes, it detects possible
  inconsistent partitioning and
\item \label{algo:solves}solves it using propagation trees (as opposed
  to propagation graphs);
\item \label{algo:competition} when required, it triggers competitions
  among neighboring partitions.
\end{inparaenum}
While (\ref{algo:most})-(\ref{algo:solves}) tackle the eventual purging of
stale notifications, (\ref{algo:competition}) tackle the eventual
delivery of the best up-to-date partitions.

To constrain the order of delivery at each process, each process
implements last win order by maintaining a vector of versions that
associates to each known source, or has-been source, with its known
local counter. It enables processes to deliver only up-to-date
$\alpha$'s that may improve their best known partition (see
Line~\ref{line:detectA}), but also to detect possible inconsistent
partitioning (see Line~\ref{line:detectB}) as labeled by III in
Figure~\ref{fig:proofB}. From a global perspective, it ensures
monotonic increase of knowledge despite the non-monotonic number of
sources. In turns, it contributes to convergence and termination, for
corresponding $\alpha$ and $\delta$ cannot follow each other in an
infinite loop.

@@

Algorithm~\ref{algo:edges} provides the instructions of \NAME that
enable dynamic consistent partitioning in dynamic networks where
processes can join or leave the system without
notification. \TODO{More.}

@@
